%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Ferns and Petals Pvt Ltd}{April 2022 -- April 2023}
    {Java Backend Developer}{Hyderabad, Telangana}
    \resumeItemListStart
        \resumeItem{Developed RESTful APIs and backend services using Spring Boot framework to support various functionalities of the e-commerce platform, including user authentication, product catalog management, order management}
        \resumeItem{Implemented database schema design and optimized SQL queries for efficient data retrieval and manipulation in MySQL and mongoDB database.}
        \resumeItem{Collaborated closely with frontend developers to integrate backend services with the user interface, ensuring seamless functionality and performance.}
        \resumeItem{Enhanced system security by implementing authentication and authorization mechanisms, as well as encryption of sensitive data to protect user privacy.}
        \resumeItem{Conducted code reviews and participated in agile development sprints to ensure code quality, adherence to coding standards, and timely delivery of features.}
        \resumeItem{Worked on performance optimization techniques such as caching, lazy loading, and asynchronous processing by using SonarQube to improve application responsiveness and scalability.}
        \resumeItem{Contributed to the design and architecture discussions, providing insights and recommendations for system improvements and enhancements.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Ventech Software Solutions Pvt Ltd}{Feb 2021 -- April 2022}
    {Software Engineer}{Hyderabad, Telangana}
    \resumeItemListStart
        \resumeItem{Developed backend solutions for a medical manufacturing company, focusing on data management and process automation.}
        \resumeItem{Designed and implemented REST APIs to support various functionalities such as data retrieval, processing, and reporting. Utilized Spring framework and Hibernate for building scalable and maintainable backend systems.}
        \resumeItem{Worked closely with stakeholders to gather requirements, analyze business needs, and translate them into technical solutions. Implemented monitoring and logging mechanisms to track system health and performance.}
        \resumeItem{Conducted thorough testing and debugging to ensure compliance with industry standards and regulations.}
    \resumeItemListEnd

\resumeSubHeadingListEnd